---
title: "How to use binomial functions"
author: "SeungHugh Jeong"
date: '2019 4 29 '
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(binomial)
```

## Binomial

The package "binomial" is a set of functions about binomial distribution calculation, and to visualize the binomial distribution table


## Basic calculation about binomial distribution

Get E(X) where X ~ B(n, p)
```{r}
bin_E <- bin_mean(trials = 100, prob = 0.5)
bin_E
```

Get Var(X) where X ~ B(n, p)
```{r}
bin_V <- bin_variance(trials = 100, prob = 0.5)
bin_V
```

Get Mode of X where X ~ B(n, p)
```{r}
bin_M <- bin_mode(trials = 100, prob = 0.5)
bin_M
```

Get skewness of X where X ~ B(n, p)
```{r}
bin_S <- bin_skewness(trials = 100, prob = 0.3)
bin_S
```

Get Kurt(X) where X ~ B(n, p)
```{r}
bin_K <- bin_kurtosis(trials = 100, prob = 0.3)
bin_K
```

Get $\binom n k$ ($nCk$)
```{r}
bin_C <- bin_choose(n = 10, k = 3)
bin_C
```

Get $P(X = k)$ for binomial
```{r}
bin_P <- bin_probability(success = 3, trials = 10, prob = 0.3)
bin_P
```


## Integrate first 5 functions

Get summary of binomial functions
```{r}
bin1 <- bin_variable(trials = 10, prob = 0.3)
bin1
summary(bin1)
```


## Table of Binomial Distribution

Get binomial distribution
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
```

Get binomial distribution with additional cumulative probability column
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
```


## Plot of Binomial Distribution

Get histogram of a binomial distribution
```{r}
plot(dis1)
```

Get graph of a cumulative distribution
```{r}
plot(dis2)
```
